
# Preface {#Preface}

```{r}
library(ggplot2);library(knitr)
```

## To Do List

+ Voir multioutput : pdf + html
+ Theme Tufte
+ Insert de Shiny
+ Faire un pdf: `Rscript -e "bookdown::render_book('index.Rmd', 'bookdown::pdf_book')"`

## A mettre en place
+ `fig_aption=TRUE` dans le Yalm, mais où ?
+ `split_by` split en plusieurs fichiers HTML (par `rmd`, `chapter` `section` `none` `chapter+number` `section+number`)
+ `split_bib= T or F` pour bib en fin de chaque page ou fin de doc

## Rappels d'édition
You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(Preface). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(RappelsProba).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [xie2015].
